DNNNNR0: How to Avoid OOTA Without Really Trying

### 2025-05-11 paper/ootavacuous.tex
ootavacuous: Page 4 wordsmithing
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Boehm and Dempsky~\cite[Section 5]{Boehm:2014:OGA:2618128.2618134}
point out that arbitrary function calls can pose challenges for any
attempt to determine semantic dependencies based solely on analysis
of the source code, using the following example:
\begin{quote}
\begin{verbatim}
y = f(x);
\end{verbatim}
\end{quote}
And it is indeed impossible to determine whether or not there is a
semantic dependency from \co{x} to \co{y} without reference to the
definition of \co{f()}.
For some definitions of \co{f()}, a semantic dependency exists, and for
others it does not.

Note that \co{f} might well be a pointer to a function, in which case
the existence of that semantic dependency might well vary at runtime as
the value of function pointer \co{f} changes.

>>>>

Boehm and Dempsky~\cite[Section 5]{Boehm:2014:OGA:2618128.2618134}
point out that arbitrary function calls can pose challenges for any
attempt to determine semantic dependencies based solely on analysis
of the source code, using the following example:
\begin{quote}
\begin{verbatim}
y = f(x);
\end{verbatim}
\end{quote}
And it is indeed impossible to determine whether or not there is a
semantic dependency from \co{x} to \co{y} without reference to the
definition of \co{f()}.
In addition, \co{f} might well be a pointer to a function, in which case
the existence of a semantic dependency from \co{x} to \co{y} might well
vary at runtime as the value of function pointer \co{f} changes.
